Mechanical automation plays a vital role in improving the efficiency and reliability of repetitive industrial operations. This project focuses on the \textbf{design, modeling, and kinematic-dynamic analysis} of a semi-automatic stick counting and packaging mechanism. The primary objective is to study and evaluate the performance of various mechanical mechanisms that can be integrated to achieve accurate stick counting, bundle formation, and packaging operations.

\vspace{12px}
The proposed system consists of a stick feeding mechanism, a purely mechanical counting mechanism, an intermittent motion transfer mechanism, and a bundle holding and packaging mechanism. The study emphasizes the application of machine design principles, including linkages, ratchet-pawl systems, cam mechanisms, and intermittent motion mechanisms, to achieve synchronized and repeatable operations without relying on complex electronic control systems.

\vspace{12px}
The project methodology involves \textbf{conceptual design, engineering calculations, 3D modeling using FreeCAD, and kinematic and dynamic analysis} to investigate the motion characteristics, force transmission, and torque requirements of the proposed mechanisms. The interaction between the individual mechanisms and their overall contribution to system performance are analyzed to identify an efficient and practical design configuration. The results of the analysis will provide insights into the feasibility and effectiveness of the proposed design, as well as potential areas for improvement and optimization in future iterations. This project aims to contribute to the field of mechanical automation by demonstrating a practical application of machine design principles in a real-world context.