\section{Technical Feasibility}
Even we will be just desinging the mechanism, still we will be study the the manufacturing process. The design will be based on standard mechanical components and manufacturing techniques to ensure that the proposed stick counting and packaging system can be feasibly produced. The components will be selected for their availability, cost-effectiveness, and suitability for the intended application. The design will also consider ease of assembly and maintenance to enhance the overall feasibility of the system.

\begin{table}[h]
\centering
\caption{Components Specifications}
\begin{tabular}{|l|l|}
\hline
Component & Typical Specification \\
\hline
Frame & Mild steel sheet / welded frame \\
Indexing mechanism & Geneva or cam-driven with hardened pins \\
Bearings & Standard ball or sleeve bearings (sizes as per shaft) \\
Feed guides & Low-friction polymer or brass inserts \\
Drive & Hand-crank or small geared motor (10-50 W) \\
Binding mechanism & Simple clamp or adhesive dispenser \\
Fasteners & Standard bolts, nuts, washers \\
\hline
\end{tabular}
\label{tab:hardware-specs}
\end{table}

\section{Modeling and Simulation Software Feasibility}
Modeling and simulation are crucial aspects of the design process. We use the FreeCAD software for 3D modeling and kinematic analysis. FreeCAD is an open-source parametric CAD software that supports the design of mechanical components and assemblies. It provides tools for creating detailed 3D models, performing simulations, and analyzing the motion of mechanisms. The software's capabilities align well with the requirements of our project, allowing us to effectively model the stick counting and packaging system, analyze its kinematics and dynamics, and optimize the design for performance and reliability. Also for the purpose of dynamic analysis, we will be using the Python programming language with libraries.
\vspace{12px}

For managing the variables, dimensions we will be using Excel spreadsheets during the design process. This will allow us to systematically organize and analyze the data related to the design parameters, material properties, and performance metrics of the proposed system. The use of Excel will facilitate efficient data management and support informed decision-making throughout the design and analysis phases of the project.

\section{Economic Feasibility}
We will go insight into the cost of materials, manufacturing, and maintenance of the proposed stick counting and packaging system. The design will prioritize cost-effectiveness by utilizing standard components and materials that are readily available in the market. The manufacturing process will be streamlined to minimize labor and production costs, while still ensuring the quality and reliability of the final product. Additionally, the system will be designed for easy maintenance to reduce long-term operational costs. The economic feasibility will be evaluated by comparing the estimated costs of the proposed system with the potential benefits it offers in terms of improved efficiency and productivity in stick counting and packaging operations.

\section{Operational Feasibility}
Operational feasibility will be assessed by evaluating the ease of use, reliability, and maintenance requirements of the proposed stick counting and packaging system. The design will focus on creating a user-friendly interface for operators, ensuring that the system can be easily operated with minimal training. Reliability will be a key consideration, with the design incorporating robust components and mechanisms to minimize downtime and ensure consistent performance. Maintenance requirements will also be addressed by designing the system for easy access to critical components, allowing for quick repairs and routine maintenance tasks. The operational feasibility will be further evaluated through testing and feedback from potential users to ensure that the system meets their needs and expectations in a real-world setting.
